%\subsection*{Sole Proprietorship\mydash\datethru{08/2013}{01/2015}}\vspace{10pt}
\employer{Sole Proprietorship}{08/2013}{01/2015}
\about{I started a small business focused on competing for DoD small business contracts. Our research interests were in off-the-shelf and open-source technologies for UAV applications. Unfortunately, program cuts and personnel reallocation at AFRL led to little to no feedback regarding our submissions.}
\duties{%
\begin{itemize}[leftmargin=*]
\item Obtain tax ID, SAM and DUNS number to meet government contract award eligibility.
\item Research topics promoted in Air Force Office of Scientific Research bulletins.
\item Define project phases and include total cost estimates.
\item Keep up-to-date information on relevant state-of-the-art technologies.
\item Explore existing image signal processing techniques.
\item Investigate image processing algorithm side effects for various image formats.
\item Experiment and prepare for prototype development using CAD software.
\item Determine
  bandwidth requirements for a mesh networked swarm UAV system for data transfer to a ground station.
\item Analyze hardware specifications to ensure compliance with FAA and FCC regulations.
\end{itemize}}
\accomplishments{%
\begin{itemize}[leftmargin=*]
\item Authored and submitted a white paper to the Air Force Research Lab titled %
  "Composite Imaging Using Low-cost Unmanned Aerial Vehicles" containing the %
  project budget analysis, milestone schedule, and scope.
\item Recruited and collaborated with two engineers.
\end{itemize}}
\partner{Miguel}{}{}{}