\begin{describe}
\subsection*{Extending Existing Knowledge}
Modified an HCS12 Dragon Development Board as a strategy to perform well in a contest in which students were asked to develop a specific program using the least number of CPU instructions. The development circuit board was 'modified' by damaging it to interrupt the signal between a specific CPU register and another board component. Severing the connection allowed the programmer to manipulate a previously inaccessible CPU register and, therefore, to use fewer instructions to complete the task. This solution required a substantial amount of research and a thorough understanding of how the Dragon Board and HCS12 processor functions.

\subsection*{Web Development}
Back-end and front-end program development:
Installed, configured, and programmed an enterprise server to utilize a popular database program, MongoDB, to store tens of gigabytes a day of live streaming financial data from multiple global sources. The program also accesses the database for data analysis and to generate graphical representations of the data using Data-Driven Documents (D3), a popular JavaScript library for creating dynamic and interactive data visualizations. The system implements NodeJS, Electron, Scalable Vector Graphics, HTML 5, Cascade Style Sheets (CSS), and BASH to create the graphical web interface. 
%Installed, configured, and programmed an enterprise server to utilize a popular database program, MongoDB, to store tens of gigabytes a day of live streaming financial data from multiple global sources. The program also accesses the database for data analysis and to generate graphical representations of the data using Data-Driven Documents (D3), a popular JavaScript library for creating dynamic and interactive data visualizations. The system also implements NodeJS, Electron, Scalable Vector Graphics, HTML 5, and Cascade Style Sheets (CSS) to create the graphical web interface. 
%Back-end and front-end program development:\break Installed, configured, and programmed an enterprise server to utilize MongoDB, a popular database program, to capture and store tens of gigabytes a day of live streaming financial data from multiple global sources for subsequent analysis. Also created a program to access the database information for algorithmic analysis and visualizations using Data-Driven Documents, a popular JavaScript library for creating dynamic and interactive data visualizations. Implemented NodeJS, Electron, Scalable Vector Graphics, HTML 5, and Cascade Style Sheets (CSS) to create the graphical user interface. -- 2017


%Modify an HCS12 Dragon Development Board to develop a method to utilize additional processor memory registers to aid in reducing the number of instructions required to complete an assigned task. Physically unbound a memory register from an external component (which afforded the programmer control of the register). This idea and approach was a compromise between meeting task requirements (minimizing the number of Assembly CPU instructions required for completion) and physically and intentionally damaging the PCB. This task required a substantial amount of research and a thorough understanding of the Dragon Board and HCS12 microchip.

%Emacs git Slackware package script author\\
%https://github.com/Derrekito/Emacs-git-for-Slackware

\end{describe}%\vspace{-12pt}
\newpage
\begin{describe}
\subsection*{Hardware Design}
\begin{itemize}
    \item Verilog - Design and Simulate a CPU with MIPS instruction set. (2011)
    \item  Design and fabricate a prototype PCB for climate control system. Verify operability of assembled PCB circuit. (2011)
\end{itemize}
\subsection*{Project Planning and Execution}
UTEP Senior Project - Review team member's solutions and monitoring progress to designated tasks. Design and produce a printed circuit board within specifications for microcontroller and subsystem components.
\subsection*{Contribution to Classroom Curriculum}
Provide technical tutorials for students in \href{http://www.ece.utep.edu/courses/web3376/EE3376.html}{EE3376 Microprocessors} to aid in program development.%\\ %2006 or 2007 
\begin{itemize}[leftmargin=*]
    \item \href{http://www.ece.utep.edu/courses/web3376/Linux.html}{Interfacing the HCS12 Using Linux}
    \item \href{http://www.ece.utep.edu/courses/web3376/MINICOM.html}{Minicom Tutorial}
    \item \href{http://www.ece.utep.edu/courses/web3376/WINE.html}{Operating AsmIDE Using WINE} %and interfacing the HCS12 Dragon Board with GNU/Linux using Minicom.\\
    \item \href{http://www.ece.utep.edu/courses/web3376/Kermit.html}{Serial Communications using "Kermit"}
\end{itemize}
\end{describe}
\section*{Social Media Links}
{\Large \faLinkedin}\hspace{12pt}\href{https://www.linkedin.com/in/derrek-landauer/}{ https://www.linkedin.com/in/derrek-landauer/}\\
{\Large \faCodepen}\hspace{10pt}\href{https://codepen.io/collection/XBWRRY/}{https://codepen.io/collection/XBWRRY/}\\
{\Large \faGithub}\hspace{12pt}\href{https://github.com/Derrekito/}{https://github.com/Derrekito/}
