\makeatletter
\def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

\begin{center}\begin{minipage}[c]{0,75\textwidth}
    \begin{flushright}%
      {\large \textbf{Landauer, Derrek}}              \\
      ~\\[-24pt]
      \hspace{1.5in}\vhrulefill{1pt} \\
      ~\\[-12pt]
    {\footnotesize
    % 1000 Wisteria Ct.,             \\
    % Albuquerque, 87116             \\
    Derrek.Landauer@gmail.com      \\
    915-873-5324}
\end{flushright}

TO: ALCON\\
DATE: 2019-06-11\\
SUBJECT: In Regards To Requisition 667702.\\[36pt]
\small
Searching for employment is a constant endeavor for a military spouse, and such opportunities can be challenging to obtain. With that in mind, an engineering candidate with a sound pedagogy from an ABET certified university may provide a leg up against the competition. I boast a robust curriculum in subjects like fiber optics, quantum mechanics, electromagnetic field theory, silicon devices design, microcontrollers, computer architecture, and operating system design.
\\\\
I also have a fondness of computer programming. My proficiency is most prominent in Python, JavaScript, BASH, and Julia; however, my literacy is comparable in assembly, ANSI C, and Java. Alongside programming, I have extensive experience with GNU/Linux and other general IT work spanning from duties of a computer/network technician to tasks customarily reserved for a senior administrator.
\\\\
In regards to engineering, my university curriculum included PCB modeling and conventional electronic circuit design. My exposure to hardware description languages required designing and simulating a processor capable of simple arithmetic computations. I've also had the opportunity to dip into operating systems programming in C exploring topics like buffer overflows and multithreaded programming.
\\\\
I do have more to offer, and I hope the attached pages provide a better sense of what that entails. Please feel free to reach out at any time. Your consideration and feedback are much appreciated.
\\\\\
    Respectfully,
\\\\
        Derrek Landauer
\end{minipage}\end{center}
